### 2020-07-10 abstract.tex
Katy comment edits

Molten salt reactors is a class of advanced nuclear reactors that promise
numerous improvements over the current fleet of largely light-water reactors.
As the world continues its transition towards low-carbon electricity
generation to combat climate change, molten salt reactors is potential
options in the near-term future for replacing fossil fuel and ageing nuclear
power plants. At the current state of development, molten salt reactors still
require extensive research to become viable. This thesis presents the latest
developments in Moltres, a simulation tool for molten salt reactors. These new
developments are: support for coupling the incompressible Navier-Stokes and
the delayed neutron precursor looping systems, and a model for
simulating decay heat from fission products at steady state and during
transients. This work demonstrates these capabilities through multiphysics
simulations of the Molten Salt Fast
Reactor concept. This work first verifies the six-group neutron diffusion
results from Moltres against continuous-energy Monte Carlo neutron transport
results from Serpent 2. The multiplication factors $k_{\text{eff}}$, delayed
neutron fractions $\beta$, temperature reactivity coefficient $\alpha_T$, and
the six-group neutron energy spectra from Moltres agreed with the high
fidelity simulation results from Serpent 2. The $k_{\text{eff}}$ values have
small discrepancies on the order of 100 pcm, which is smaller than the
$-256.7$ pcm discrepancy reported in literature with the same six-group
neutron diffusion approach. The decay heat model shows an expected flattening
of the temperature distribution due to the movement and dispersion of the
decay heat precursors throughout the primary coolant loop. This work also
demonstrates and verifies steady state and
transient multiphysics simulations of the Molten Salt Fast Reactor. The
transient scenarios under study were unprotected instances of reactivity
insertion, loss of heat sink, loss of flow, and pump overspeed. The steady
state and transient results were verified against results from another paper
that presented results for the same cases. The steady-state temperature and
velocity distributions, and the peak neutron flux showed good agreement with
the literature results. Minor differences in the delayed neutron precursor
distribution and the in-core delayed neutron fraction were explainable with
the differences in the handling of turbulence in the models. In three of the
transient results (reactivity insertion, loss of heat sink, and pump
overspeed), Moltres reproduced the expected magnitude and pattern of the
reactor response to these transient initiators.
The loss of flow results showed greater discrepancies that are attributed
to differences in the fluid dynamics modeling in Moltres and the other models.
Through the verification studies, this work has also identified avenues
for further Moltres software development.

>>>>

Molten salt reactors is a class of advanced nuclear reactors that promise
numerous improvements over the current fleet of largely light-water reactors.
As the world continues its transition towards low-carbon electricity
generation to combat climate change, molten salt reactors is a potential
option in the near-term future for replacing fossil fuel and ageing nuclear
power plants. At the current state of development, molten salt reactors still
require extensive research to become viable. This thesis presents the latest
developments in Moltres, a simulation tool for molten salt reactors. These
new developments are: support for coupling the incompressible Navier-Stokes
and the delayed neutron precursor looping systems, and a model for
simulating decay heat from fission products at steady state and during
transients. This work demonstrates these capabilities through multiphysics
simulations of the Molten Salt Fast
Reactor concept. This work first verifies the six-group neutron diffusion
results from Moltres against continuous-energy Monte Carlo neutron transport
results from Serpent 2. The multiplication factors $k_{\text{eff}}$, delayed
neutron fractions $\beta$, temperature reactivity coefficient $\alpha_T$, and
the six-group neutron energy spectra from Moltres agreed with the high
fidelity simulation results from Serpent 2. The $k_{\text{eff}}$ values have
small discrepancies on the order of 100 pcm, which is smaller than the
$-256.7$ pcm discrepancy reported in literature with the same six-group
neutron diffusion approach. The decay heat model shows an expected flattening
of the temperature distribution due to the movement and dispersion of the
decay heat precursors throughout the primary coolant loop. This work also
demonstrates and verifies steady state and
transient multiphysics simulations of the Molten Salt Fast Reactor. The
transient scenarios under study were unprotected instances of reactivity
insertion, loss of heat sink, loss of flow, and pump overspeed. The steady
state and transient results were verified against results from another paper
that presented results for the same cases. The steady-state temperature and
velocity distributions, and the peak neutron flux showed good agreement with
the literature results. Minor differences in the delayed neutron precursor
distribution and the in-core delayed neutron fraction were explainable with
the differences in the handling of turbulence in the models. In three of the
transient results (reactivity insertion, loss of heat sink, and pump
overspeed), Moltres reproduced the expected magnitude and pattern of the
reactor response to these transient initiators.
The loss of flow results showed greater discrepancies that are attributed
to differences in the fluid dynamics modeling in Moltres and the other models.
Through the verification studies, this work has also identified avenues
for further Moltres software development.

### 2020-07-10 model.tex
Katy comment edits

Serpent 2 \cite{leppanen_serpent_2014} is a continuous-energy Monte Carlo
neutron transport application under
active development led by the VTT Technical Research Centre of Finland. It was
created in 2004 for group constant generation in lattice geometries, and has
since grown to support more general capabilities. Serpent 2 is highly
parallelizable, supporting both MPI and OpenMP parallel programming APIs. It
has also been validated and verified against experimental data and other well
established codes \cite{leppanen_calculation_2014}.

@@

As mentioned in the Chapter \ref{chap:msr}, the fuel salt loop is divided into
two regions, the central core region where most of the fissions take place,
and the outer loop region where the heat exchanger is located. The central
core region specifically refers to the central region indicated by
the red box in Figure \ref{fig:core}. The outer loop is simplified
into a 1-D pipe as it is a subcritical region and its main purposes are: to
introduce an out-of-core residence time for the \glspl{DNP}, and to contain
the heat removal kernel to simulate the heat exchanger.
Accordingly, this section provides separate descriptions for the governing
equations in the central core region and the outer loop region. There is also
a third region comprised of the blanket salt, the NiCrW Hastelloy reflectors, 
and other material. This region is important for capturing a more accurate
estimate of neutron leakage than would
imposing fixed albedo neutron flux boundary conditions.

@@

In addition to the intrinsic molecular viscosity in the \gls{INS} equations,
this thesis introduces an
eddy viscosity term to approximate turbulent flow effects. The current
implementation of the Navier-Stokes module does not have a turbulence model
such as the \gls{RANS} models used in the Polimi and TUDelft models
\cite{fiorina_modelling_2014}. Thus, this work uses
a zeroth-order approximation of the eddy viscosity based on the results
reported in the Polimi/TUDelft models. The eddy viscosity is assumed to be 40
Pa$\cdot$s. Despite the simplicity of this assumption, the resulting flow profile is
similar to flow profile in the Polimi and TUDelft models at steady state.

@@

Table \ref{table:loopbc} summarizes the boundary conditions for all variables
on the inlet and outlet of the 1-D outer loop region.

>>>>

Serpent 2 \cite{leppanen_serpent_2014} is a continuous-energy Monte Carlo
neutron transport application under
active development led by the VTT Technical Research Centre of Finland. It was
created in 2004 for group constant generation in lattice geometries, and has
since grown to support more general capabilities. Serpent 2 is highly
parallelizable, supporting both MPI and OpenMP parallel programming APIs. It
has also been validated and verified against experimental data and other well
established neutron transport applications \cite{leppanen_calculation_2014}.

@@

As mentioned in the Chapter \ref{chap:msr}, the fuel salt loop is divided into
two regions, the central core region where most of the fissions take place,
and the outer loop region where the heat exchanger is located. The red box in
Figure \ref{fig:core} indicates the central core region. The outer loop is
simplified into a 1-D pipe as it is a subcritical region. Its main purposes
are to introduce an out-of-core residence time for the \glspl{DNP} and to
contain the heat removal kernel to simulate the heat exchanger.
Accordingly, this section provides separate descriptions for the governing
equations in the central core region and the outer loop region. There is also
a third region comprised of the blanket salt, the NiCrW Hastelloy reflectors, 
and other material.

@@

In addition to the intrinsic molecular viscosity in the \gls{INS} equations,
this thesis introduces an eddy viscosity term, $\mu_t$, to approximate
turbulent flow effects. The current implementation of the Navier-Stokes module
does not have a turbulence model. The options for turbulence modeling in
\gls{CFD} include direct numerical simulations (DNS) and large eddy
simulations (LES) for higher fidelity flow simulations, \gls{RANS} methods for
balanced compromises between accuracy and computational speed, and lumped
parameter and sub-channel methods for even faster performance with greater
accuracy costs \cite{moorthi_review_2018}. The Polimi and TUDelft models used
\gls{RANS} methods to model salt flow \cite{fiorina_modelling_2014}. This work
uses a zeroth-order approximation of $\mu_t$ based on the calculated $\mu_t$
values reported in the Polimi and TUDelft models. The models
predicted spatial $\mu_t$ values ranging from 0-110 Pa$\cdot$s, with most
of the core lying in the 30-50 Pa$\cdot$s range. Thus, the present work uses
the approximated value $\mu_t=$ 40 Pa$\cdot$s. Despite the simplicity of this
approximation, the resulting flow profile is similar to flow profile in the
Polimi and TUDelft models at steady state.

@@

Table \ref{table:loopbc} summarizes the boundary conditions for all variables
on the inlet and outlet of the 1-D outer loop region. The inlet boundary
conditions are all Dirichlet boundary conditions. The inlet boundary values
are set by the outflow from the central core region that this inlet is
connected to in the actual reactor geometry. The outlet boundary conditions
are all outflow boundary conditions as shown in the table.
